Overview

### 2021-05-31 overview_gh.Rmd
testing shinytest on CI, ref #10
Bump version; update NEWS; ready for CRAN
Make abstracts_keyatm the 'default' topic model to save space; various fixes for CRAN

`abstracts_stm` is an example topic model trained with the data `abstracts` using the `stm` package. Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` , LDA/CTM models from `topicmodels`,  Biterm Topic Models from `BTM`, Keyword Assisted Topic Models from `keyATM`, and seeded LDA models from `seededlda`. Although not strictly a topic model, Naive Bayes models from `quanteda.textmodels` are also supported. See the section on [Naive Bayes](#about-naive-bayes) for more information.

```{r}
library(oolong)
library(stm)
library(quanteda)
library(dplyr)
```

```{r example}
abstracts_stm
```

@@

```{r createtest}
oolong_test <- wi(abstracts_stm, userid = "Hadley")
oolong_test
```

@@

```{r wsi1}
oolong_test <- wsi(abstracts_stm, userid = "Garrett")
oolong_test
```

@@

For example, `abstracts_stm` was generated with the corpus `abstracts$text`

@@

```{r createtest2}
oolong_test <- ti(abstracts_stm, abstracts$text, userid = "Julia")
oolong_test
```

@@

@@

```{r step0, eval = FALSE}
dfm(abstracts$text, tolower = TRUE, stem = TRUE, remove = stopwords('english'), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_hyphens = TRUE) %>% dfm_trim(min_docfreq = 5, max_docfreq = 1000) %>% dfm_select(min_nchar = 3, pattern = "^[a-zA-Z]+$", valuetype = "regex") -> abstracts_dfm
docvars(abstracts_dfm, "title") <- abstracts$title
abstracts_dfm %>% convert(to = "stm", omit_empty = FALSE) -> abstracts_stm
abstracts_stm <- stm(abstracts_stm$documents, abstracts_stm$vocab, data =abstracts_stm$meta, K = 10, seed = 42)
```

@@

```{r step1}
oolong_test_rater1 <- witi(abstracts_stm, abstracts$text, userid = "Yihui")
```

@@

Suppose `newsgroup_nb` is a Naive Bayes model trained on a subset of the classical [20 newgroups] dataset.

>>>>

`abstracts_keyatm` is an example topic model trained with the data `abstracts` using the `keyATM` package. Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` , LDA/CTM models from `topicmodels`,  Biterm Topic Models from `BTM`, Keyword Assisted Topic Models from `keyATM`, and seeded LDA models from `seededlda`. Although not strictly a topic model, Naive Bayes models from `quanteda.textmodels` are also supported. See the section on [Naive Bayes](#about-naive-bayes) for more information.

```{r}
library(oolong)
library(keyATM)
library(quanteda)
library(dplyr)
```

```{r example}
abstracts_keyatm
```

@@

```{r createtest}
oolong_test <- wi(abstracts_keyatm, userid = "Hadley")
oolong_test
```

@@

```{r wsi1}
oolong_test <- wsi(abstracts_keyatm, userid = "Garrett")
oolong_test
```

@@

For example, `abstracts_keyatm` was generated with the corpus `abstracts$text`

@@

```{r createtest2}
oolong_test <- ti(abstracts_keyatm, abstracts$text, userid = "Julia")
oolong_test
```

@@

Preprocess and create a document-feature matrix

```{r, eval = FALSE}
dfm(abstracts$text, tolower = TRUE, stem = TRUE, remove = stopwords('english'), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_hyphens = TRUE) %>% dfm_trim(min_docfreq = 3, max_docfreq = 500) %>% dfm_select(min_nchar = 3, pattern = "^[a-zA-Z]+$", valuetype = "regex") -> abstracts_dfm
```

@@

```{r step0, eval = FALSE}
require(keyATM)
abstracts_keyatm <- keyATM(keyATM_read(abstracts_dfm), no_keyword_topics = 0, keywords = abstracts_dictionary, model = "base", options = list(seed = 46709394))
```

@@

```{r step1}
oolong_test_rater1 <- witi(abstracts_keyatm, abstracts$text, userid = "Yihui")
```

@@

Suppose `newsgroup_nb` is a Naive Bayes model trained on a subset of the classic [20 newsgroups] dataset.
